\begin{center}
\mbox{}

\bigskip

\LARGE\textsc{Praying through the tabernacle}

\end{center}

\pagestyle{empty}
\setlength{\parindent}{0em}

\section{The Gates (Thanksgiving)}


\begin{quote}
    ``Enter into his gates with thanksgiving\ldots{}.'' (Psalms~100:4)
\end{quote}

Take time to thank the Lord for His many blessings!


\section{The Court (Praise)}

\begin{quote}
``\dots{}and into his courts with praise: be thankful unto him, and bless his name.'' (Psalms~100:4)
\end{quote}

Take time to praise God for who He is, for what He has done and what He does.



\section{Brazen Altar (Confession)}

\begin{quote}
``If we confess our sins, he is faithful and just to forgive us our sins,
    and to cleanse us from all unrighteousness.'' (I John 1:9)
\end{quote}

\begin{itemize}
\item Take time to confess your sins and ask for forgiveness.
    Personal repentance is necessary every time you seek to come into God’s presence.
\item ``Create in me a clean heart, O God; and renew a right spirit within me.'' (Psalm 51:10)
\end{itemize}


\section{Brazen Laver – Place of cleansing (Meditating on the Word of God)}


\begin{quote}
``\ldots{} Christ loved the church and gave himself up for her,
    that he might sanctify her, having cleansed her by the washing
    of water with the word.''  (Ephesians~5:25-27)
\end{quote}

Ask the Lord to cleanse you from sin and meditate on His Word.
Remember the many promises that He has given us in His Word.



\section{Golden Lampstand\\(Jesus the light of the world)}


\begin{quote}
``Then spake Jesus again unto them, saying, I am the light of the world:
    he that followeth me shall not walk in darkness,
    but shall have the light of life.'' (John 8:12)
\end{quote}

Take the time to pray for all the ministries that God puts on your heart.
For the church, pastors, the leadership of the church, Bible study groups,
prayer groups, missionaries\ldots{}


\section{Table of showbread (Personal needs)}

\begin{quote}
``And Jesus said unto them, I am the bread of life:
    he that cometh to me shall never hunger;
    and he that believeth on me shall never thirst.'' (John 6:35)
\end{quote}

Take the time to pray for your personal needs,
both physical and spiritual (peace, finances, health, faith\ldots{}).


\section{Golden Altar of Incense\\(Intercession)}

\begin{quote}
``Let my prayer be set forth before thee as incense;
    and the lifting up of my hands as the evening sacrifice.'' (Psalm 141:2)
\end{quote}

Incense was offered daily, just as we are to pray daily and without ceasing.
Take time to intercede for others.


\section{Holy of Holies (adoration)}

Only the High Priest was permitted to enter the Most Holy Place
once a year, on the Day of Atonement.
When Jesus died on the cross, the veil that separated the Holy Place
and the Holy of Holies was miraculously torn in two.
Thank God that through Jesus' sacrifice salvation is extended to all,
and anyone can enter into God’s presence and commune with Him.

Take time to worship Him in spirit and in truth!
